### 2016-09-16 GPCE2016/sections/Overview.tex
space
Final version.

\section{A Running Example: Animals}\label{sec:ep}
\begin{figure*}
\centering
\saveSpaceFig
\begin{tabular}{c|c}
\includegraphics[height=3.3cm]{pdfs/PegasusDetail.pdf}\hspace{0pt} &
\begin{minipage}{7cm}
\vspace{-95pt}
\lstinputlisting[linerange=6-13]{../UseMixinLombok/src/pegasus/simple/java8/Main.java}% APPLY:linerange=PEGASUS_JAVA
%basicstyle=\ttfamily\scriptsize
\end{minipage}
\end{tabular}
\caption{The animal system (left: complete structure, right: code for simplified animal system).}\label{fig:pegasus}
\saveSpaceFig
\end{figure*}

This section illustrates how our programming style, supported by
\mixinAnn{}, enables powerful programming idioms based on multiple
inheritance and type refinements.  We propose a standard example:
\Q@Animal@s with a 2-dimensional \Q@Point2D@ representing their
\Q@location@, subtypes \Q@Horses@, \Q@Bird@s, and \Q@Pegasus@.
Birds can \Q@fly@, thus their locations need to be 3-dimensional
\Q@Point3D@s (field type refinement). We model \Q@Pegasus@
(a well-known creature in Greek mythology) as a kind of
\Q@Animal@ with the skills of both \Q@Horse@s and \Q@Bird@s (multiple
inheritance). A simple class diagram illustrating the basic system is
given on the left side of Figure~\ref{fig:pegasus}.
%\footnote{Some
%  research argues in favor of using subtyping for modeling taxonomies,
%  other research argues against this practice, we do not wish to take
%  sides in this argument, but to provide an engaging example.}

@@

@@

\vspace{-5pt}
\para{\Q@Point2D@ with object interfaces}
This obvious ``constructor'' code is generated by the \mixin
annotation.  By annotating the interface \Q@Point2D@, a variation of the shown
static method \texttt{of} will be generated, mimicking the functionality of a
simple-minded constructor. \mixin first looks at the abstract methods and detects
what the fields are, then generates an \Q@of@ method with one parameter for each
of them. We can just write:

@@

\lstinputlisting[linerange=70-79]{../UseMixinLombok/src/pegasus/TestAnimal.java}% APPLY:linerange=BIRD
%Interface \texttt{Point3D} extends \texttt{Point2D} with a new abstract method
%\texttt{int z()} (treated as a getter for member field \texttt{z}). Note that
%the return type of various methods (e.g. with- methods, getters) get refined
%either by covariant method overriding or automatically by our annotation
%processor. Besides \emph{with}, other methods (including \emph{clone},
%\emph{of}) also do type-refinements automatically.

@@

\begin{figure}
\saveSpaceFig
\lstinputlisting[linerange=88-114]{../UseMixinLombok/src/pegasus/TestAnimal.java}% APPLY:linerange=GENERATED_POINT3D
\caption{Generated boilerplate code.}
\label{fig:boilerplate}
\saveSpaceFig
\end{figure}

@@

\begin{figure*}
\saveSpaceFig
\centering
\hspace{.01in}{%\fontsize{8}{10}\selectfont
\begin{tabular}{|l|l|l|l|}
\hline
& \textbf{Operation}  & \textbf{Example}                  & \textbf{Description } \\ \hline
\multirow{4}{*}{\parbox{2.3cm}{State operations (for a field \texttt{x})}} & \textbf{``fields''/getters}        &   \Q@int x()@                  & Retrieves value from field \texttt{x}.          \\ \cline{2-4}
& {\bf withers}        &   \Q@Point2D withX(int val)@                & Clones
object; updates field \texttt{x} to \texttt{val}.             \\ \cline{2-4}
& \textbf{setters}        & \Q@void x(int val)@ & Sets the field
\texttt{x} to a  new value \texttt{val}.        \\ \cline{2-4}
& \textbf{fluent setters}        & \Q@Point2D x(int val)@ &Sets the field
\texttt{x} to \texttt{val} and returns \texttt{\this}.  \hspace{-.1in}         \\ \hline
\multirow{3}{*}{Other operations} &
\textbf{factory methods} &
%\begin{tabular}{l}
\Q@static Point2D of(int _x,int _y)@
%\end{tabular}
 & Factory method (generated).        \\
\cline{2-4}
& \textbf{functional updaters}        & \Q@Point3D with(Point2D val)@
& Updates all matching fields in \texttt{val}.        \\ \hline
%\cline{2-4}
%& \textbf{imperative updaters}        & \Q@Point3D set(Point2D val)@ &
%Set all matching fields in \texttt{val}.        \\ \hline
\end{tabular}
}
\caption{Abstract state operations for a field \texttt{x}, together with other operations, supported by the \mixin
  annotation. }

\label{fig:abstractstate}

\end{figure*}

@@

\lstinputlisting[linerange=83-83]{../UseMixinLombok/src/pegasus/TestAnimal.java}% APPLY:linerange=PEGASUS

@@

\lstinputlisting[linerange=70-79]{../UseMixinLombok/src/pegasus/TestAnimal.java}% APPLY:linerange=BIRD

\lstinputlisting[linerange=83-83]{../UseMixinLombok/src/pegasus/TestAnimal.java}% APPLY:linerange=PEGASUS

>>>>

\section{A Running Example: Animals}\label{sec:ep}
This section illustrates how our programming style, supported by
\mixinAnn{}, enables powerful programming idioms based on multiple
inheritance and type refinements.  We propose a standard example:
\Q@Animal@s with a 2-dimensional \Q@Point2D@ representing their
\Q@location@, subtypes \Q@Horses@, \Q@Bird@s, and \Q@Pegasus@.
Birds can \Q@fly@, thus their locations need to be 3-dimensional
\Q@Point3D@s (field type refinement). We model \Q@Pegasus@
(a well-known creature in Greek mythology) as a kind of
\Q@Animal@ with the skills of both \Q@Horse@s and \Q@Bird@s (multiple
inheritance). A simple class diagram illustrating the basic system is
given on the left side of Figure~\ref{fig:pegasus}.
%\footnote{Some
%  research argues in favor of using subtyping for modeling taxonomies,
%  other research argues against this practice, we do not wish to take
%  sides in this argument, but to provide an engaging example.}

@@

\begin{figure*}[t]
\centering
% \saveSpaceFig
\vspace{-1ex}
\begin{tabular}{c|c}
\includegraphics[height=3.3cm]{pdfs/PegasusDetail.pdf}\hspace{0pt} &
\begin{minipage}{7cm}
\vspace{-95pt}
\lstinputlisting[linerange=6-13]{../UseMixinLombok/src/pegasus/simple/java8/Main.java}% APPLY:linerange=PEGASUS_JAVA
%basicstyle=\ttfamily\scriptsize
\end{minipage}
\end{tabular}
\caption{The animal system (left: complete structure, right: code for simplified animal system).}\label{fig:pegasus}
\saveSpaceFig
\end{figure*}

@@

\vspace{-3pt}
\para{\Q@Point2D@ with object interfaces}
This obvious ``constructor'' code is generated by the \mixin
annotation.  By annotating the interface \Q@Point2D@, a variation of the shown
static method \texttt{of} will be generated, mimicking the functionality of a
simple-minded constructor. \mixin first looks at the abstract methods and detects
what the fields are, then generates an \Q@of@ method with one parameter for each
of them. We can just write:

@@

\lstinputlisting[linerange=70-76]{../UseMixinLombok/src/pegasus/TestAnimal.java}% APPLY:linerange=BIRD
%Interface \texttt{Point3D} extends \texttt{Point2D} with a new abstract method
%\texttt{int z()} (treated as a getter for member field \texttt{z}). Note that
%the return type of various methods (e.g. with- methods, getters) get refined
%either by covariant method overriding or automatically by our annotation
%processor. Besides \emph{with}, other methods (including \emph{clone},
%\emph{of}) also do type-refinements automatically.

@@

\begin{figure}
\vspace{-1.5ex}
\lstinputlisting[linerange=85-111]{../UseMixinLombok/src/pegasus/TestAnimal.java}% APPLY:linerange=GENERATED_POINT3D
\caption{Generated boilerplate code.}
\label{fig:boilerplate}
\saveSpaceFig
\end{figure}

@@

\begin{figure*}[t]
% \saveSpaceFig
\vspace{-1ex}
\centering
\hspace{.01in}{%\fontsize{8}{10}\selectfont
\begin{tabular}{|l|l|l|l|}
\hline
& \textbf{Operation}  & \textbf{Example}                  & \textbf{Description } \\ \hline
\multirow{4}{*}{\parbox{2.3cm}{State operations (for a field \texttt{x})}} & \textbf{``fields''/getters}        &   \Q@int x()@                  & Retrieves value from field \texttt{x}.          \\ \cline{2-4}
& {\bf withers}        &   \Q@Point2D withX(int val)@                & Clones
object; updates field \texttt{x} to \texttt{val}.             \\ \cline{2-4}
& \textbf{setters}        & \Q@void x(int val)@ & Sets the field
\texttt{x} to a  new value \texttt{val}.        \\ \cline{2-4}
& \textbf{fluent setters}        & \Q@Point2D x(int val)@ &Sets the field
\texttt{x} to \texttt{val} and returns \texttt{\this}.  \hspace{-.1in}         \\ \hline
\multirow{3}{*}{Other operations} &
\textbf{factory methods} &
%\begin{tabular}{l}
\Q@static Point2D of(int _x,int _y)@
%\end{tabular}
 & Factory method (generated).        \\
\cline{2-4}
& \textbf{functional updaters}        & \Q@Point3D with(Point2D val)@
& Updates all matching fields in \texttt{val}.        \\ \hline
%\cline{2-4}
%& \textbf{imperative updaters}        & \Q@Point3D set(Point2D val)@ &
%Set all matching fields in \texttt{val}.        \\ \hline
\end{tabular}
}
\caption{Abstract state operations for a field \texttt{x}, together with other operations, supported by the \mixin
  annotation. }

\label{fig:abstractstate}
\saveSpaceFig
\end{figure*}

@@

\lstinputlisting[linerange=80-80]{../UseMixinLombok/src/pegasus/TestAnimal.java}% APPLY:linerange=PEGASUS

@@

\lstinputlisting[linerange=70-76]{../UseMixinLombok/src/pegasus/TestAnimal.java}% APPLY:linerange=BIRD

\lstinputlisting[linerange=80-80]{../UseMixinLombok/src/pegasus/TestAnimal.java}% APPLY:linerange=PEGASUS
